---
title: "in-class exercise"
author: "Xingjian Yan"
date: "2/26/2021"
output: github_document
---
#####1.Make a table that describes each plane. It should have a column for tailnum, another column for average arrival delay, and another for the year the plane was manufactured.

```{r}
library(dplyr)
library(nycflights13)
flights %>% 
  group_by(tailnum) %>%
  summarize(missing_delay = mean(arr_delay, na.rm = T)) %>%
  left_join(planes) %>%
  select(tailnum:year) %>%
  head(10)

```

#####2.Make a table where each row is a day of the year. The first column is the date. The 2:4 columns give the number of (scheduled) departures from EWR, LGA, and JFK.

```{r}
library(tidyr)
flights %>%
  mutate(date = as.Date(time_hour)) %>%
  group_by(origin, date) %>%
  summarize(deps = n()) %>%
  pivot_wider(names_from = origin, values_from = deps) %>%
  head(10)
  
```

#####3.Make a table where each row is a day of the year. Each destination airport is a column. The elements (day x destination) give the number of flights to that destination. What should NA’s be?
```{r}
flights %>%
  mutate(date = as.Date(time_hour)) %>%
  group_by(date,dest) %>%
  summarize(deps = n()) %>%
  pivot_wider(names_from = dest, values_from = deps) %>% head(10)

```
*NAs should be zeros, it means that no flights at that day flied to the destination.*